---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/franckpicard/hawkes_genomics/branch/main/graph/badge.svg)](https://app.codecov.io/gh/franckpicard/hawkes_genomics?branch=main)
[![R-CMD-check](https://github.com/franckpicard/hawkes_genomics/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/franckpicard/hawkes_genomics/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

[HawkGenomics website](https://franckpicard.github.io/hawkes_genomics/)

# Hawkes genomics

R package to Estimate parameters for a hawkes model over spatial positions [using this c++ implementation](https://github.com/fgindraud/hawkes/tree/master).

## Requirement

A C++ compiler supporting C++14 is required:

- g++ >= 5.0
- clang++ >= 3.4
- for any other compiler, check that it supports the -std=c++14 flag

R >= 4.3 (the package may works on older version of R)

## Installation

You need the package `remotes` to install `hawkesGenomics` from this repository

```r
install.packages("remotes")
```

Then you can install `hawkesGenomics` with this command

```r
remotes::install_git("https://github.com/franckpicard/hawkes_genomics", force = T)
```

## Example

We are going to analyse a subset of the replication origin on the chromosme 1
of hg19.

```{r}
library("hawkesGenomics")
```

## preprocess data

```{r}
beds <- preprocess_bed(
  files = c(
    system.file("extdata", "oris.bed.gz", package = "hawkesGenomics"),
    system.file("extdata", "CGI.bed.gz", package = "hawkesGenomics"),
    system.file("extdata", "G4plus.bed.gz", package = "hawkesGenomics")
  ),
  names = c("Oris", "CGI", "G4plus")
)
```

## hawkes computation

```{r}
res <- compute_hawkes_histogram(
  files = beds$preprocess_beds,
  names = beds$names,
  K = 5,
  delta = 1e4
)
```

## plot data

```{r}
plot_histogram(res, K = 5, delta = 1e4)
```

```{r}
plot_convolution(res, width = beds$interval_size, K = 5, delta = 1e4)
```

